%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\multilang
  {1}
  {\cvsection{Education}}
  {\cvsection{Ausbildung}}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\multilang
  {1}
  {\cventry
    {B.Sc. in Computer Science} % Degree
    {University of Bremen} % Institution
    {Bremen, Germany} % Location
    {Oct. 2016 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA Aug. 2018: 1.22 on a scale from 1.0 (best) to 4.0 (passing) with Electrical Engineering as a voluntary minor}
    %    \item {Received full scholarship of the Studienstiftung (German Academic Scholarship Foundation)}
        \item {This term: participation in the university's RoboCup Major SPL Team B-Human, focus on perception and machine learning}
      \end{cvitems}
    }
  }{\cventry
    {B.Sc. in Informatik} % Degree
    {Universität Bremen} % Institution
    {Bremen, Deutschland} % Location
    {Okt. 2016 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Durschschnittsnote Aug. 2018: 1.22}
    %    \item {Vollstipendium der Studienstiftung des deutschen Volkes}
        \item {Teilnahme im RoboCup Team B-Human der Universität in der Liga Major SPL, Fokus im Bereich perception und machine learning}
      \end{cvitems}
    }
  }
    
%---------------------------------------------------------
\multilang
  {0}
  {\cventry
    {Abitur} % Degree
    {Gymnasium Damme} % Institution
    {Damme, Germany} % Location
    {Jul. 2007 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 1.8 on a scale from 1.0 (best) to 4.0 (passing) with scientific profile (Physics, Math, English, Geography, Computer Science)}
        \item {Participated in the robotics club}
      \end{cvitems}
    }
  }{\cventry
    {Abitur} % Degree
    {Gymnasium Damme} % Institution
    {Damme, Deztschland} % Location
    {Jul. 2007 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Durchschnittsnote: 1.8 mit naturwissenschaftlichem Profil (Physik, Mathe, Englisch, Erdkunde, Informatik)}
        \item {Teilnahme in der Roboter AG}
      \end{cvitems}
    }
  }

%---------------------------------------------------------
\end{cventries}
