%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Assistant} % Job title
    {DLR e.V. (German Aerospace Center)} % Organization
    {Bremen, Germany} % Location
    {Oct. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researching redundant, error tolerant computer networks for the ReFEx (Reusability Flight Experiment) project in the Department of Guidance, Navigation and Control}
        \item {\url{https://www.dlr.de/irs/en/desktopdefault.aspx/tabid-11350}}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Student Assistant} % Job title
    {DFKI (German Researchcenter for AI) GmbH} % Organization
    {Bremen, Germany} % Location
    {Nov. 2016 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the embedded software for safety-critical optical interconnected sensor-systems serving as artificial robotic skin}
        \item {Implemented sensor drivers, communication protocol and UART/CAN bootloader for the ST STM32 controller family in C}
        \item {Developed a Qt GUI in C++ to visualize the data of multiple connected sensors on a screen}
        \item {Set up ROS with a Velodyne LIDAR and a ZED stereo camera on the head of the AILA2 robot, implemented ROS hardware driver and simple object tracking to test the servo motors and the sensors.}
        \item {Implemented a CNN in Tensorflow to detect if a person is sitting properly on a car seat fitted with a grid of 120 optical sensors.}
        \item {Implemented the embedded software on a new optical tactile sensor field and helped validating the sensors in a deep sea pressure chamber.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Developer} % Job title
    {BSAB GmbH} % Organization
    {Damme, Germany} % Location
    {Jul. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of the software for an modular embedded electrical wireless socket nut magazine for industrial/manufacturing purposes.}
        \item {The system is capable to detect if a socket nut is placed at a defined position (inductive sensing or RFID)}
        \item {Based on the nut that is taken out of place, the device communicates to the screwing controller via CAN, RS232 or TCP/IP}
        \item {The device with the nut selector might be a mobile wireless unit. There can be multiple mobile devices, communicating to one base station, which emulates a physical connection to each of the mobile devices to the screw controller.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Internship} % Job title
    {DFKI (German Researchcenter for AI) GmbH} % Organization
    {Bremen, Germany} % Location
    {Oct. 2015 - Dez. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Familiarized with the Xilinx FPGA toolchain and VHDL by implementing basic things like PWM, UART, I2C}
        \item {Fixed a bug in the VHDL driver of a camera module which prevented using the camera with the highest resolution.}
        \item {Implementated a Canny Edge filter and a Circle-Hough-Transformation on a FPGA development kit with camera in VHDL.}
        \item {Bridged the VHDL modules to an emulated Microblaze CPU on the FPGA}
        \item {Implemented a Qt GUI to visualize the data in real time}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
